% Format of Work Details-
% {\bf Position, Company, location} \hfill 
    % {time period}\\
        % responsibilities involved

{\textbf{Software Engineer} at \textbf{Twilio}, Czechia} 
    \hfill {\em Nov 2020 - Present}\\
    {L2 Software Engineer, Flex Insights Real-Time} \hfill  {Oct 2021 - Present}\\
    {L1 Software Engineer, Flex Insights} \hfill            {Nov 2020 - Sep 2021}\\
    {Intern Software Engineer, Flex Insights} \hfill        {Apr - Oct 2020}
    \begin{itemize}
        \item Participated in the design and Private Beta implementation of a highly-distributed real-time insights solution for Customer Engagement Platform that used Kafka streams and OLAP-aggregation for building stateful models in near real time, providing end-to-end refresh latency of under 30s. \textbf{Key Technologies:} Java, Docker, Kafka, AWS, Druid, OLAP-aggregation
        \item Participated in post-Private Beta delivery and maintenance of a low latency, highly available distributed system that used Kafka Streams to aggregate data in near real time, providing end-to-end data refresh latency of under 10 seconds. \textbf{Key Technologies}: Java, Docker, Kafka, AWS
        \item Collaborated with team members, including SDET, to introduce Mutation Testing and enhance the unit test strength. Expanded testing capabilities by adding Integration Tests using mocking tools, End-to-End tests, as well as non-functional testing such as chaos and load tests. \textbf{Key technologies:} Buildkite, Jenkins, PiTest, Cucumber, Selenium, TypeScript, Mockito, Docker
        \item Frequently served as a \textbf{guest engineer} for various teams, gaining exposure to diverse infrastructures and deepening understanding of interdependent components within the company.
        \item Led the implementation of Infrastructure-as-Code (IaC) practices within the organization, assuming responsibility as the primary point person for managing team resources. \textbf{Key Technologies:} Terraform, Infrastructure-as-Code (IaC)
        \item As \textbf{Interview Panelist}: Conducted technical and non-technical interviews and assessments for prospective candidates, evaluating their skills and qualifications for the organization.
        \item As \textbf{Editorial Board Member}: Contributed to the creation and publication of the AI/ML Practitioners Guild newsletter, providing insights and updates on industry trends and innovations. Additionally, assisted in organizing seminars and hackathons to promote community engagement and professional development.
        \item As \textbf{Onboarding Coordinator}: Managed and optimized the onboarding process for new team members, including those from sister teams, by providing guidance on company policies and procedures, and ensuring that they had the necessary resources and knowledge to perform their job functions effectively. Ensured a smooth transition into their roles and onto our infrastructure to promote productivity and team integration.
    \end{itemize}